### 2021-05-04 Supplementary_Material/Missing_data.Rmd
just some edits on a plot form supp. mat

colnames(t) <- c("Breeding system","Compatibility system",
         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
         "Flower number per plant", "Floral display width", "Flower width", "Flower length","Style length", "Ovule number", 
         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar quantitative")

@@

percentage.plot <- missing.values %>%
  ggplot() +
  geom_bar(aes(x = reorder(key, desc(pct)), 
               y = pct, fill=isna), 
           stat = 'identity', alpha=0.8) +
  scale_x_discrete(limits = levels) + theme_bw()+
  scale_fill_manual(name = "", 
                    values = c('steelblue', 'tomato3'), labels = c("Present", "Missing")) +
  coord_flip() +
  labs(title = "Percentage of missing values", x =
         'Variables', y = "% of missing values")

>>>>

colnames(t) <- c("Breeding system","Compatibility system",
         "Autonomous selfing qualitative","Autonomous selfing quantitative", "Flower shape", "Flower symmetry", 
         "Flower number per plant", "Inflorescence width", "Flower width", "Flower length","Style length", "Ovule number", 
         "Life form", "Lifespan","Plant height","Nectar qualitative","Nectar quantitative")

@@

percentage.plot <- missing.values %>%
  ggplot() +
  geom_bar(aes(x = reorder(key, desc(pct)), 
               y = pct, fill=isna), 
           stat = 'identity', alpha=0.8) +
  scale_x_discrete(limits = levels) + theme_bw()+
  scale_fill_manual(name = "", 
                    values = c('#57a340', '#d24513'), labels = c("Present values", "Missing values")) +
  coord_flip() +
  labs(title = "", x =
         '', y = "")+  scale_y_continuous(labels = function(x) paste0(x*1, "%")) +
  theme(panel.border = element_rect(colour = "black", fill=NA, size=1))
